---
output: 
  pdf_document:
    includes:
      in_header: header.tex
params:
  trs: trs
  revert: FALSE
sansfont: Calibri light

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F,
                      warning = F)
```

***

\begin{vwcol}[widths={0.3,0.7},
 sep=.8cm, justify=flush,rule=0pt,indent=1em] 
   \null \vfill
  \includegraphics[width=.2\textwidth]{./Acceso/LOGO.jpg}
  \vfill \null
  
\newpage
  
  \null \vfill
  \section{\fontsize{50}{15}\selectfont Full Body}
  \vfill \null
 \end{vwcol}

``` {r echo = FALSE}
id.code <- gsub("[^0-9.]", "",  unique(params$trs$ID))
transaction.type <- unique(params$trs$Transaccion)

if (transaction.type == 'Venta') {
  subtitle <- 'Proforma'
} else if (transaction.type == 'Nota de credito') {
  subtitle <- 'Nota de Crédito'
} else {
  subtitle <- paste0('Documento de ', 
                     transaction.type)
}

subtitle <- paste0(subtitle, 
                   ' [\\#', 
                   id.code,
                   ']')
```

\section{\fontsize{25}{15}\selectfont \hfil `r subtitle`\hfil}
\bigskip
\bigskip


``` {r echo = FALSE}
  
if (unique(params$trs$Transaccion) %in% c('Venta')) {
  sale.detail <- rbind(params$trs[, c('Producto',
                                'Cantidad',
                                'Precio',
                                'Total')],
                       c('Total',
                         '',
                         '',
                         sum(params$trs$Total)))
  
  inf.gen <- as.data.frame(t(params$trs[1, names(params$trs) %in% c('Documento.Interno',
                                                                    'Fecha',
                                                                 'Medio.Pago',
                                                                 #'Origen',
                                                                 'Destino'#,
                                                                 #'Relacion'
                                                                 )]))
  
  row.names(inf.gen)[row.names(inf.gen) == 'Destino'] <- 'Cliente'
  
} else if (unique(params$trs$Transaccion) %in% c('Nota de credito')) {
  sale.detail <- rbind(params$trs[, c('Producto',
                                'Cantidad',
                                'Precio',
                                'Total')],
                       c('Total',
                         '',
                         '',
                         sum(params$trs$Total)))
  
  inf.gen <- as.data.frame(t(params$trs[1, names(params$trs) %in% c('Documento.Interno',
                                                                    'Fecha',
                                                                 'Medio.Pago',
                                                                 'Origen'#,
                                                                 #'Destino',
                                                                 #'Relacion'
                                                                 )]))
  
  row.names(inf.gen)[row.names(inf.gen) == 'Origen'] <- 'Cliente'
  
} else if (unique(params$trs$Transaccion) %in% c('Proveedor Recepcion',
                                                 'Proveedor Devolucion')) {
    sale.detail <- rbind(params$trs[, c('Producto',
                                'Cantidad',
                                'Precio',
                                'Total')],
                       c('Total',
                         '',
                         '',
                         sum(params$trs$Total)))
  
  inf.gen <- as.data.frame(t(params$trs[1, names(params$trs) %in% c('Documento.Interno',
                                                                    'Fecha',
                                                                 #'Origen',
                                                                 'Destino',
                                                                 'Razon'
                                                                 )]))
  
  row.names(inf.gen)[row.names(inf.gen) == 'Destino'] <- 'Proveedor'
  
  
} else if (unique(params$trs$Transaccion) %in% c('Separacion')){
  
  sale.detail <- rbind(params$trs[, c('Producto',
                                'Cantidad')])
  
  sale.detail <- rbind(sale.detail,
                       data.frame('Producto' = 'Total',
                                  'Cantidad' = NA_integer_))
  
  inf.gen <- as.data.frame(t(params$trs[1, names(params$trs) %in% c('Documento.Interno',
                                                                    'Fecha',
                                                                 #'Origen',
                                                                 'Destino',
                                                                 'Razon'
                                                                 )]))
  
  row.names(inf.gen)[row.names(inf.gen) == 'Destino'] <- 'Cliente'
  
} else {
  sale.detail <- rbind(params$trs[, c('Producto',
                                'Cantidad')])
  
  sale.detail <- rbind(sale.detail,
                       data.frame('Producto' = 'Total',
                                  'Cantidad' = NA_integer_))
  
  inf.gen <- as.data.frame(t(params$trs[1, names(params$trs) %in% c('Documento.Interno',
                                                                    'Fecha',
                                                                 #'Origen',
                                                                 'Destino'
                                                                 )]))
}

# add total quantity of products
sale.detail$Cantidad[dim(sale.detail)[1]] <- sum(as.numeric(sale.detail$Cantidad[-dim(sale.detail)[1]]))

# formatting changes
row.names(inf.gen)[row.names(inf.gen) == 'Documento.Interno'] <- 'D.I'


```

``` {r echo = FALSE, results = 'asis'}

library(knitr)
library(xtable)
t1 <- knitr::kable(sale.detail,
               format = 'latex',
               booktabs = T)

t2 <- knitr::kable(inf.gen,
             format = 'latex', 
             col.names = 'Info',
             booktabs = T)

cat(c("\\begin{table}[!htb]
    \\begin{minipage}[t]{.5\\linewidth}
      \\vspace{0pt}
      \\centering",
        t1,
    "\\end{minipage}%
    \\begin{minipage}[t]{.5\\linewidth}
      \\vspace{0pt}
      \\centering",
        t2,
    "\\end{minipage} 
\\end{table}"
))

```



\newcommand*\wildcard[2][5cm]{\vspace*{2cm}\parbox{#1}{\hrulefill\par#2}}


\begingroup
  \centering
  \wildcard{}
  \hspace{1cm}
  \wildcard{}
  \par
\endgroup



***
``` {r echo = FALSE}
rm(sale.detail)
rm(inf.gen)
```